Title

### 2018-08-31 thesis/paper/paper.tex
Improved one-of

\subsection{One-of (Q21510859)}
The one-of constraint limits the values a property may use to a set of given values.

\begin{table}[H]
\caption{One-of constraint (Q21510859)}
\begin{tabularx}{\textwidth}{ ll X}
\hline
Required data & constrained statement \\
\hline
Qualifiers & \makecell{allowed values (P2305) -- 1..* \\ values that may be used in the constrained statement} \\
\hline
Violation & \makecell{constrained statement with a value unequal to all allowed values} \\
\hline
Dependency & constrained statement \\
\hline
Rule features & inequality \\
\hline
\end{tabularx}
\end{table}

Modelling the one-of constraint requires a rule finding a statementEDB with the constrained property whose value is unequal to all allowed values, meaning the inequality between each value of constrained statements and all allowed values must be given.

@@

\subsection{One-of (Q21510859)}
The one-of constraint fits in the pattern established by the previous two constraints and disallows certain property-value combinations. Inequality is pre-processed between all values of constrained statements. With \(A\) the set of allowed values the rules for triple, qualifier and reference are respectively:
\begin{equation*}
\begin{split}
\text{violation\_triple}&(S, I, \text{propertyConstant}, V) \leftarrow \\
&\text{statementEDB}(S, I, \text{propertyConstant}, V) \wedge \text{unequal}(\{A\}, V)
\end{split}
\end{equation*}
\begin{equation*}
\begin{split}
\text{violation\_qualifier}&(S, \text{propertyConstant}, V) \leftarrow \\
&\text{qualifierEDB}(S, \text{propertyConstant}, V) \wedge \text{unequal}(\{A\}, V)
\end{split}
\end{equation*}
\begin{equation*}
\begin{split}
\text{violation\_reference}&(S, \text{propertyConstant}, V) \leftarrow \\
&\text{referenceEDB}(S, H, \text{propertyConstant}, V) \wedge \text{unequal}(\{A\}, V)
\end{split}
\end{equation*}

>>>>

\subsection{One-of (Q21510859)}
\subsubsection{Constraint}
The \emph{one-of} constraint limits the values of a constraint statement, qualifier or reference to a set of given values.

\begin{table}[H]
\caption{One-of constraint (Q21510859)}
\begin{tabularx}{\textwidth}{ ll X}
\hline
Required data & constrained statements, qualifiers and references \\
\hline
Qualifiers & \makecell{\emph{allowed values} (P2305) -- 1..* \\ values that may be used as objects of a constrained statement} \\
\hline
Violation & \makecell{constrained statement with a value unequal to all allowed values} \\
\hline
Rule features & inequality \\
\hline
\end{tabularx}
\end{table}

\subsubsection{Rules}
The one-of constraint fits in the pattern established by the previous two constraints and disallows certain property-value combinations in statements, qualifiers and references. Inequality is established between all \emph{allowed values} and the values of statements, qualifiers and references, respectively. With \(A\) the set of allowed values the rules for triple, qualifier and reference are:
\begin{align*}
\text{violation\_triple}(S, I, \text{propertyConstant}, V) &\leftarrow \\
\text{statementEDB}(S, I, &\text{propertyConstant}, V) \wedge \text{unequal}(\{A\}, V) \\
\text{violation\_qualifier}(S, \text{propertyConstant}, V) &\leftarrow \\
\text{qualifierEDB}(S, &\text{propertyConstant}, V) \wedge \text{unequal}(\{A\}, V) \\
\text{violation\_reference}(S, \text{propertyConstant}, V) &\leftarrow \\
\text{referenceEDB}(S, H, &\text{propertyConstant}, V) \wedge \text{unequal}(\{A\}, V)
\end{align*}

@@
